How to Make a Proceedings Paper Submission

### 2022-12-14 code/4_paper/manuscript/manuscript.Rmd
setting up cogsci paper

---
title             : "Is It Language or Is It Culture? Re-examining Cross-Cultural Similarity Judgments Using Lexical Co-Occurrence"
shorttitle        : "Re-examining Cross-Cultural Similarity Judgments Using Lexical Co-Occurrence"

author: 
  - name          : "Khuyen Le"
    affiliation   : "1,2"
    corresponding : yes    # Define only one corresponding author
    email         : "khuyenle@stanford.edu"

affiliation:
  - id            : "1"
    institution   : "Psychology Department"
  - id            : "2"
    institution   : "University of California, San Diego"

abstract: |
  Is “cow” more closely related to “grass” or “chicken”? Speakers of different languages judge similarity in this context differently, but why? One possibility is that cultures co-varying with these languages induce variation in conceptualizations of similarity. Specifically, East Asian cultures may promote reasoning about thematic similarity, by which cow and grass are more related whereas Western cultures may bias similarity judgments toward taxonomic relations, like cow-chicken. This difference in notions of similarity is the consensus interpretation for cross-cultural variation in this paradigm. We consider, and provide evidence for, an alternative possibility, by which notions of similarity are equivalent across contexts, but the statistics of the environment vary. On this account, similarity judgments are guided by co-occurrence in experience, and observing or hearing about cows and grass or cows and chickens more often could induce preferences for the relevant grouping and account for apparent differences in notions of similarity across contexts.

  <!-- https://tinyurl.com/ybremelq -->

keywords          : "similarity, culture, language, semantics, lexical co-occurrence, variation"
wordcount         : "150"

bibliography      : ["r-references.bib", "references/references.bib"]

floatsintext      : yes
figurelist        : no
tablelist         : yes
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
header-includes:
  - \raggedbottom

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf

---

@@

r_refs("r-references.bib")
r_refs("references/packages.bib")

@@

# Methods 
```{r get exclusion results from 1_exclusions.Rmd}
source("../1_exclusions/1_exclusionsCN.Rmd")
source("../1_exclusions/1_exclusionsUS.Rmd")
source("../1_exclusions/1_exclusionsVN.Rmd")
```

```{r demog_E, TODO: move outside, include = F}
demog <- c("demog-dropdown", "demog-multi-choice", "demog-free-response", "demog-multi-select")
df.demog_E <- df.resp_E %>%
  filter(trial_type %in% demog) 
#write.csv(data_demog, "data_anon_demog_0201.csv")

AGE = 97 #index for age answer
GENDER = 115 #index for gender answer
split_responses <- function(responses) {
  responses <- as.character(responses)
  response_list <- unlist(strsplit(responses, ',|:'))
  response_list <- response_list[seq(1, length(response_list))]
  response_list <- gsub("}", "", response_list)
  response_list <- gsub("\"", "", response_list)
  return(response_list)
}

get_age <- Vectorize(function(responses) {
  responses <- split_responses(responses)
  if(responses[AGE-1] != "A0") {warnings("cannot find age answer")}
  else{return (responses[AGE])}
})

get_gender <- Vectorize(function(responses) {
  responses <- split_responses(responses)
  if(responses[GENDER-1] != "A1") {warnings("cannot find gender answer")}
  else{return (responses[GENDER])}
})

df.age_gender_E <- df.demog_E %>%
  filter(variable_type == "demog_age_gender_ethnic") %>%
  select(subject, responses) %>%
  mutate(age = as.numeric(get_age(responses))) %>%
  mutate(age = as.numeric(age)) %>%
  mutate(gender = get_gender(responses))

df.age_gender_E_summ <- df.age_gender_E %>%
  summarize(mean_age = mean(age), 
            median_age = median(age), 
            sd_age = sd(age))
```

```{r demog_V, TODO: move outside, include = F}
demog <- c("demog-dropdown", "demog-multi-choice", "demog-free-response", "demog-multi-select")
df.demog_V <- df.resp_V %>%
  filter(trial_type %in% demog)

AGE = 97 #index for age answer
GENDER = 115 #index for gender answer
split_responses <- function(responses) {
  responses <- as.character(responses)
  response_list <- unlist(strsplit(responses, ',|:'))
  response_list <- response_list[seq(1, length(response_list))]
  response_list <- gsub("}", "", response_list)
  response_list <- gsub("\"", "", response_list)
  return(response_list)
}

get_age <- Vectorize(function(responses) {
  responses <- split_responses(responses)
  if(responses[AGE-1] != "A0") {warnings("cannot find age answer")}
  else{return (responses[AGE])}
})

get_gender <- Vectorize(function(responses) {
  responses <- split_responses(responses)
  if(responses[GENDER-1] != "A1") {warnings("cannot find gender answer")}
  else{return (responses[GENDER])}
})

df.age_gender_V <- df.demog_V %>%
  filter(variable_type == "demog_age_gender_ethnic") %>%
  select(subject, responses) %>%
  mutate(age = as.numeric(get_age(responses))) %>%
  mutate(age = as.numeric(age)) %>%
  mutate(gender = get_gender(responses))

df.age_gender_V_summ <- df.age_gender_V %>%
  summarize(mean_age = mean(age), 
            median_age = median(age), 
            sd_age = sd(age))
```

```{r demog_M, TODO: MOVE outside, include = F}
demog <- c("demog-dropdown", "demog-multi-choice", "demog-free-response", "demog-multi-select")
df.demog_M <- df.resp_M %>%
  filter(trial_type %in% demog) 
#write.csv(data_demog, "data_anon_demog_0201.csv")

AGE = 97 #index for age answer
GENDER = 115 #index for gender answer
split_responses <- function(responses) {
  responses <- as.character(responses)
  response_list <- unlist(strsplit(responses, ',|:'))
  response_list <- response_list[seq(1, length(response_list))]
  response_list <- gsub("}", "", response_list)
  response_list <- gsub("\"", "", response_list)
  return(response_list)
}

get_age <- Vectorize(function(responses) {
  responses <- split_responses(responses)
  if(responses[AGE-1] != "A0") {warnings("cannot find age answer")}
  else{return (responses[AGE])}
})

get_gender <- Vectorize(function(responses) {
  responses <- split_responses(responses)
  if(responses[GENDER-1] != "A1") {warnings("cannot find gender answer")}
  else{return (responses[GENDER])}
})

df.age_gender_M <- df.demog_M %>%
  filter(variable_type == "demog_age_gender_ethnic") %>%
  select(subject, responses) %>%
  mutate(age = as.numeric(get_age(responses))) %>%
  mutate(age = as.numeric(age)) %>%
  mutate(gender = get_gender(responses))

df.age_gender_M_summ <- df.age_gender_M %>%
  summarize(mean_age = mean(age), 
            median_age = median(age), 
            sd_age = sd(age))
```
## Participants
We recruited `r length(unique(df.ppts_finished_E$subject))` participants from the US, `r length(unique(df.ppts_finished_V$subject))` participants from Vietnam, and `r length(unique(df.ppts_finished_M$subject))` participants from mainland China. US participants were recruited through snowball sampling seeded with Stanford email lists, Vietnam participants were recruited through snowball sampling seeded with Vietnam-based student groups on Facebook, and mainland China participants were recruited through snowball smapling seeded with group chats on WeChat. US participants were compensated with $5 gift certificates (USD), VN participants received 50,000₫ (VND) in phone credit, and mainland China participants received 25CNY through WeChat credit transfer.

We excluded `r length(unique(df.ppts_finished_E$subject)) - length(unique(df.ppts_att_E$subject))` US participants, `r length(unique(df.ppts_finished_V$subject)) - length(unique(df.ppts_att_V$subject))` Vietnam participants, and `r length(unique(df.ppts_finished_M$subject)) - length(unique(df.ppts_att_M$subject))` China participants who did not answer all attention checks correctly. We followed 4 exclusion criteria that aim to retain only participants who are influenced by one culture: (1) non-native speakers of English and Vietnamese, respectively, (2) fluent in at least one of the other two study languages (Vietnamese for US participants, English for Vietnamese participants and Chinese participants), (3) have lived outside of the test country (US, Vietnam, or China) for more than two years, and (4) have significant international experience (more than 6 international experiences of 2 days or longer.) We did not use a particular criterion for a language if it would exclude 25% or more of any one sample. In this round of exclusion, we excluded `r length(unique(df.ppts_att_E$subject)) - length(unique(df.resp_E$subject))` US, `r length(unique(df.ppts_att_V$subject)) - length(unique(df.resp_V$subject))` Vietnam participants, and `r length(unique(df.ppts_att_M$subject)) - length(unique(df.resp_M$subject))` China participants. After these exclusions, the US sample included `r length(unique(df.resp_E$subject))` participants (`r df.age_gender_E %>% filter(gender == "Male") %>% count()`M, `r df.age_gender_E %>% filter(gender == "Female") %>% count()`F, `r df.age_gender_E %>% filter(gender == "Non-binary") %>% count()` non-binary, `r df.age_gender_E %>% filter(gender == "Decline to answer") %>% count()` other), with mean age = `r round(df.age_gender_E_summ$mean_age, 2)` (SD = `r round(df.age_gender_E_summ$sd_age, 2)`) and median age = `r df.age_gender_E_summ$median_age`. The Vietnam sample included `r length(unique(df.resp_V$subject))` participants (`r df.age_gender_V %>% filter(gender == "Nam") %>% count()`M, `r df.age_gender_V %>% filter(gender == "Nữ") %>% count()`F), with mean age = `r round(df.age_gender_V_summ$mean_age, 2)` (SD = `r round(df.age_gender_V_summ$sd_age, 2)`) and median age = `r df.age_gender_V_summ$median_age`. The China sample included `r length(unique(df.resp_M$subject))` participants (`r df.age_gender_M %>% filter(gender == "男性") %>% count()`M, `r df.age_gender_M %>% filter(gender == "女性") %>% count()`F), with mean age = `r round(df.age_gender_M_summ$mean_age, 2)` (SD = `r round(df.age_gender_M_summ$sd_age, 2)`) and median age = `r df.age_gender_M_summ$median_age`.

Notably, we lost a majority of our Vietnam participants (more than 60%) in the attention check exclusion. One reason we suspect why this might have happened is because our Vietnam participants are less familiar with research surveys and attention check questions, and thus might have thought too much about the attention check questions. We carried out an exploratory analysis where we used a less stringent attention check exclusion (covered in the final part of the Results & Analysis section). To preview our findings for this analysis, we did not find any difference in significant results when compared with the main analysis.

## Stimuli
We adapted stimuli from previous studies to create a set of test triads consisting of a cue, with one thematic and one taxonomic match option. For example, “cow,” “grass,” and “chicken,” where “cow” is the cue, “grass” is the thematic match, and “chicken” the taxonomic match. We included 105 such triads, a superset including triads pulled from supplemental information and in-text examples across the literature, and others that we adapted or created (see SI for the full list of stimuli and sources). We selected triads on the basis of cultural familiarity in the US, Vietnam, and China. The triads were originally in English; they were translated to Vietnamese and Mandarin by a fluent bilingual speaker in each language. The translations were then checked for accuracy after backtranslation to English by another fluent bilingual in each language who was naive to the original English versions.

Each participant completed all 105 triads in sets of 21 trials at a time (10 test triads, 10 filler triads, and 1 attention check per page), by selecting the match most related to the cue (“Which thing is most closely related to the bolded item?” or "Thu nào liên quan nhat voi thu đuoc in đam?"). The test triads were presented with 105 filler triads mixed in, to obscure the taxonomic-thematic two-answer forced choice structure of the test stimuli and reduce the likelihood that participants would become aware of the design. The filler triads were groups of three semantically related words, but where the match options were not distinguished by thematic vs. taxonomic similarity, e.g., cue “bird” with match options “lizard” and “toad.” Additionally, we included 10 attention check trials, which were formatted like the test and filler triads but included an instruction instead of a cue item, e.g., “Choose wife” with match options “wife” and “husband.” In total, each participant completed 210 similarity judgments and 10 attention check questions, with triads presented in randomized orders that varied between subjects.

## Corpus model 
Our general approach is to build a model of similarity that is based on collocation counts in each language.

### Raw lexical co-occurrences
To give an intuition for our model, consider the cow-grass-chicken triad: we counted how many times “cow” and “grass” co-occur within a window of text in each corpus, and compare this to how many times “cow” and “chicken” co-occur. Our similarity prediction is then proportional to the relative frequency of these pairs. For example, if the thematic cow-grass match accounts for 30% of collocations for this triad (with cow-chicken making up the other 70%), then our model predicts, correspondingly, that 30% of responses to the triad will be grass, and the other 70% chicken. We then use a mixed-effects regression to evaluate how well each corpus collocate model predicts participants’ similarity judgments, across triads and languages.

#### Collocate retrieval and coding
For our English co-occurrence metric, we used the online interface of the Corpus of Contemporary American English [@COCA] to retrieve collocation counts. We recorded the raw count of times that any cue-match pair (e.g., cow-grass or cow-chicken) co-occur in a window of 19 words, which is the maximum window size in the online interface, and closest to the sentence co-occurrence metric in our VI corpus collocation counts.

To determine Vietnamese co-occurrence, we used the raw frequency of sentence co-occurrences from a subset of the Vietnamese corpus in the Leipzig Corpora Collection [@VICorpus]; this corpus includes 70 million Vietnamese sentences, but our corpus data comes from a 1 million sentence subset for which co-occurrence counts are available for download. Vietnamese makes very frequent use of compositional morphology but the written language  uses spacing to delineate syllable boundaries rather than word boundaries. Accordingly, collocate searches returned instances of both target terms and many morphologically related, but distinct, words. We included in our counts any instances of the target term or close semantic neighbors containing the same morpheme(s) as long as they entailed a likely literal reference to the target term. For example, our search for collocates of the term “gà” (chicken) also returned “gà mái,” a distinct word for female chickens. Despite being a different word, “gà mái” both includes the morpheme for “chicken” and entails reference to a chicken. Accordingly, instances of both “gà” and “gà mái” were included in our collocate count for “chicken.” Some compounds do not meet this criteria, and were excluded from collocate counts. For example “trái cây” (tree.fruits) includes the same syllable as the word “cây” (tree), but refers to fruit that comes from trees, not the trees themselves, and was therefore excluded from our collocate counts for “tree.”

We were unable to obtain a Mandarin corpus with similar number of sentences as the aforementioned English and Vietnamese corpora, hence we did not include any analysis based on raw lexical co-occurrences with Mandarin.

#### Collocate similarity model
From the raw co-occurrence counts of each triad, we calculated the thematic co-occurrence ratio as the number of thematic co-occurrences over the sum of thematic and taxonomic co-occurrences. We did this for both the English and Vietnamese corpus co-occurrence counts. In this way, we obtained predictions for 73 of 105 triads from the Vietnamese corpus and 104 of 105 triads from English. We therefore limited all analyses reported here to the subset of triads for which our corpus-based model can make meaningful predictions, meaning triads that have at least one non-zero collocate count (either thematic or taxonomic match). We replaced any remaining zero collocate counts with $\epsilon$ to account for sparsity in the corpus data. We then tested whether these simple relative frequency models predict US and VN responding.

### Cosine distance of word vectors
To give an intuition for our model, consider again the cow-grass-chicken triad: we retrieved word vectors for "cow" and "grass", and calculate the cosine distance between these vectors. Similarly, we retrieved vectors for "cow" and "chicken" and calculate the cosine distance between them. Our similarity prediction is then inversely proportional to the cosine distance of these pairs. This is because a larger cosine distance means the word vectors are further apart, and thus the words are less similar. For example, if the cosine distance of thematic cow-grass is 0.7 and the cosine distance of taxonomic cow-chicken is 0.3, then our model predicts, correspondingly, that 30% of responses to the triad will be grass, and the other 70% chicken. We then use a mixed-effects regression to evaluate how well each corpus model predicts participants’ similarity judgments, across triads and languages.

#### Collocate retrieval
We use the fastText pre-trained models of English, Mandarin, and Vietnamese in @Grave2018. These models are trained on Common Crawl and Wikipedia using We distribute pre-trained word vectors for 157 languages, trained on Common Crawl and Wikipedia using fastText. These models were trained using a Continuous Bag of Words (CBOW) with position-weights and a window of size 5. The models use character n-grams of length 5 and 10  negative examples.From the aforementioned models, we retrieve the word vectors (dimension 300) for each word we are interested in.

#### Collocate similarity model
From the word vectors, we calculated the cosine distance between each cue-thematic match (thematic cosine distance) and cue-taxonomic match (taxonomic cosine distance), using the spatial.distance.cosine function from the SciPy package [@2020SciPy]. We then calculated the thematic cosine distance proportion as thematic cosine distance over the sum of taxonomic cosine distance and thematic cosine distance. We did this for all three corpora. We were able to obtain predictions for all triads in all languages.

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.

# Results
```{r combine corpus and behavior data, include = F}
#source("../2_combine/2_combine.Rmd")
df <- read.csv("../../data/data_USCNVN_ENZHVI.csv")
```

## Do we extend previous work reporting a preference for taxonomic matching in the US and thematic matching in Asia?

```{r warning=FALSE, include=FALSE, paged.print=TRUE}
df.country <- df %>%
  group_by(subject, country) %>%
  summarize(theme_resp_percent = mean(responses_theme, na.rm = T))

df.country_sum <- df.country %>%
  group_by(country) %>%
  summarize(mean_theme_resp_percent = mean(theme_resp_percent), 
            sd_theme_resp_percent = sd(theme_resp_percent))

fit.country = glmer(responses_theme ~ country + (1 | subject) + (country | triad), 
                    data = df, 
                    family = "binomial")
summary(fit.country) 
fit.country.anova = Anova(fit.country, type=3)

fit.country_EN_VN = glmer(responses_theme ~ country + (1 | subject) + (country | triad), 
                    data = df %>% filter(country != "China"),
                    family = "binomial")
summary(fit.country_EN_VN) 
```
The group means of proportion of thematic response in mainland China is the highest (M = `r round((df.country_sum %>% filter(country == "China"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "China"))$sd_theme_resp_percent, 2)`), followed by the groups means in Vietnam (M = `r round((df.country_sum %>% filter(country == "Vietnam"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "Vietnam"))$sd_theme_resp_percent, 2)`), which is slightly higher than that of the US (M = `r round((df.country_sum %>% filter(country == "US"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "US"))$sd_theme_resp_percent, 2)`).

```{r echo=FALSE, warning=FALSE, fig.cap="Proportion of thematic responses by country. Only US-China responding comparison shows a siginficant difference. We could not extend this to US-Vietnam responding comparison."}

#show violin plot
ggplot(df.country,
       mapping = aes(x = factor(country, levels=c("China", "US", "Vietnam")), 
                     y = theme_resp_percent, 
                     color = factor(country, levels=c("China", "US", "Vietnam")))) +
  geom_violin() +
  geom_jitter(height = 0, 
              alpha = 0.3) +  
  stat_summary(fun.data = "mean_cl_boot", 
               geom = "pointrange") + 
  labs(y = "Proportion Thematic Chosen", 
       x = "Country", 
       color = "Country") + 
  scale_color_manual(values=c("#D63230", "#1C77C3", "#F39237"))
```

```{r correlation of country response, echo=FALSE, warning=FALSE}
#US-China, US-Vietnam, China-Vietnam
df.triad_country <- df %>%
  group_by(triad, country) %>%
  summarize(emp_theme_prop = mean(responses_theme))

df.triad_country <- pivot_wider(data = df.triad_country, 
                                names_from = country, 
                                values_from = emp_theme_prop)
plotUSCN = ggplot(data = df.triad_country,
                  mapping = aes(x = US, 
                                y = China, 
                                label = triad)) +
   geom_text() + 
   geom_smooth(method = "lm") +
   labs(x = "Proportion Thematic Chosen (US)", 
        y = "Proportion Thematic Chosen (China)") + 
   xlim(0, 1) + 
   ylim(0, 1) + 
  theme(axis.title = element_text(size=rel(0.75)))

plotUSVN = ggplot(data = df.triad_country,
                  mapping = aes(x = US, 
                                y = Vietnam, 
                                label = triad)) +
   geom_text() + 
   geom_smooth(method = "lm") +
   labs(x = "Proportion Thematic Chosen (US)", 
        y = "Proportion Thematic Chosen (Vietnam)") + 
   xlim(0, 1) + 
   ylim(0, 1)  + 
  theme(axis.title = element_text(size=rel(0.75)))

plotCNVN = ggplot(data = df.triad_country,
                  mapping = aes(x = Vietnam,
                                y = China, 
                                label = triad)) +
   geom_text() + 
   geom_smooth(method = "lm") +
   labs(x = "Proportion Thematic Chosen (Vietnam)", 
        y = "Proportion Thematic Chosen (China)") + 
   xlim(0, 1) + 
   ylim(0, 1)  + 
  theme(axis.title = element_text(size=rel(0.75)))

corr.USCN = apa_print(cor.test(df.triad_country$US, 
                  df.triad_country$China, na.rm=T))

corr.USVN = apa_print(cor.test(df.triad_country$US, 
                  df.triad_country$Vietnam, na.rm=T))

corr.CNVN = apa_print(cor.test(df.triad_country$China, 
                  df.triad_country$Vietnam, na.rm=T))
```

```{r warning = F, fig.width = 8, fig.cap="Correlation between proportion thematic chosen by US-China participants, US-Vietnam participants, and China-Vietnam participants. All three comparisons show strong correlation, suggesting a strong signal of universality across cultural contexts regarding similarity judgments"}
plotUSCN + plotUSVN + plotCNVN +
  plot_layout(ncol = 3)
```

With a Pearson correlation test, we observed high correlations between thematic responding across all three countries. The proportion of US thematic responding is strongly correlated with thematic responding in China, `r corr.USCN$full_result`. The proportion of US thematic responding is strongly correlated with thematic responding in Vietnam, `r corr.USVN$full_result`. Likewise, the proportion of China thematic response is strongly correlated with thematic responding in Vietnam, `r corr.CNVN$full_result`. This points to a strong signal of universality across cultural contexts regarding similarity judgments.

```{r USCN effect size comparison, include=FALSE}
USCN_cohen <- cohen.d(df.triad_country$China, df.triad_country$US)
```

For comparison with previous work, we also included an effect size comparison for the difference in US-China thematic response data (though this was not a planned analysis). The effect size for this analysis was d = `r USCN_cohen$estimate`, a small effect size. This is smaller than the effect size from @Ji2004, even when we are unable to make a direct comparison. Calculating the effect size from the ANOVA reported in @Ji2004 between US participants tested in English and mainland China participants tested in English (both groups tested in the US) yields a Cohen's d = 0.81. @Ji2004 reported that mean thematic response for mainland China participants tested in Mandarin Chinese is higher than for those tested in English, so the effect size for a comparison between mainland China participants tested in Mandarin Chinese and US participants tested in English (parallel to our comparison) would likely have yielded an even larger effect size than 0.814. It is possible that we failed to replicate the magnitude of effect from @Ji2004 because the previous study calculated their dependent variable as frequency of thematic responses minus frequency of taxonomic responses, whereas our dependent variable is proportion of thematic response over total number of responses.

To test for cross-context differences in similarity judgments between the countries, we ran a mixed-effects logistic regression predicting triad responding (taxonomic or thematic) with country (US, China, or Vietnam) as a fixed effect. As random effects, we included an intercept per subject and one per triad, as well as by-triad random slopes for country to account for variation in the country effect across triads. In R syntax, the model is: response ~ country + (1 | subject) + (country | triad).

Overall, there is a significant effect of country on proportion of thematic responses ($\chi^2$(`r fit.country.anova["country", "Df"]`) = `r round(fit.country.anova["country", "Chisq"], 2)`, p < .001). However, this effect is driven by the difference between US and China responding ($\beta$ = `r round(fixef(fit.country)["countryUS"], 2)`, p < .001). There is no statistical difference between the Vietnam and China responding ($\beta$ = `r round(fixef(fit.country)["countryVietnam"], 2)`, p = `r round(as.data.frame(summary(fit.country)[["coefficients"]])["countryVietnam", "Pr(>|z|)"], 2)`), and the US and Vietnam responding ($\beta$ = `r round(fixef(fit.country_EN_VN)["countryVietnam"], 2)`, p = `r round(as.data.frame(summary(fit.country_EN_VN)[["coefficients"]])["countryVietnam", "Pr(>|z|)"], 3)`).

On this analysis, we do not find support that the US-China tendencies toward taxonomic and thematic responding (respectively) extend to the US-Vietnam comparison. Accordingly, we cannot speak to overall biases toward thematic responding across Asian cultural contexts broadly, but we do replicate the differences documented by @Ji2004 between the US and China. However, in our corpus model comparison, we do find evidence for different, more fine-grained variation in similarity judgments between the US and Vietnam.

## Can the differences in similarity judgments between English, Mandarin and Vietnamese speakers be explained by variation in lexical statistics?
### Is responding in each cultural context predicted by the corresponding lexical statistics (raw co-occurrences and cosine distance)? 
```{r Pearson correlation between raw co-occurrences of corpora and responding, warning=FALSE, include=FALSE}

#raw co-occurrences
df.triad_country_freq <- df %>%
  filter(!(triad %in% triads_omit)) %>% # omit triads that do not have meaningful prediction (at least 1 non-zero prediction in both languages)
  group_by(triad, country, theme_freq_prop_E, theme_freq_prop_V, theme_freq_prop_M) %>%  # not working 
  summarize(emp_theme_prop = mean(responses_theme))
df.triad_country_freq   #sanity

df.triad_country_freq_E <- df.triad_country_freq %>%
  filter(country == "US")

#plotting English corpus against US responding data
plotE = ggplot(data = df.triad_country_freq_E,
        mapping = aes(x = emp_theme_prop,
                     y = theme_freq_prop_E,
                     label = triad)) +
   geom_text() +
   geom_smooth(method = "lm") +
   labs(x = "Proportion Thematic Chosen (US)",
        y = "Proportion Thematic Predicted (English)")
plotE

df.triad_country_freq_V <- df.triad_country_freq %>%
  filter(country == "Vietnam")

#plotting Vietnamese corpus against VN responding data
plotV = ggplot(data = df.triad_country_freq_V,
        mapping = aes(x = emp_theme_prop,
                     y = theme_freq_prop_V,
                     label = triad)) +
   geom_text() +
   geom_smooth(method = "lm") +
   labs(x = "Proportion Thematic Chosen (Vietnam)",
        y = "Proportion Thematic Predicted (Vietnamese)")
plotV

df.triad_country_freq_M <- df.triad_country_freq %>%
  filter(country == "China")

#plotting China corpus against CN responding data
plotM = ggplot(data = df.triad_country_freq_M,
        mapping = aes(x = emp_theme_prop,
                     y = theme_freq_prop_M,
                     label = triad)) +
   geom_text() +
   geom_smooth(method = "lm") +
   labs(x = "Proportion Thematic Chosen (China)",
        y = "Proportion Thematic Predicted (Chinese)")
plotM

#Pearson correlation between corpus and responding
corr.E = apa_print(cor.test(df.triad_country_freq_E$emp_theme_prop,
                  df.triad_country_freq_E$theme_freq_prop_E, na.rm=T))
corr.E

corr.V = apa_print(cor.test(df.triad_country_freq_V$emp_theme_prop,
                  df.triad_country_freq_V$theme_freq_prop_V, na.rm=T))
corr.V

corr.M = apa_print(cor.test(df.triad_country_freq_M$emp_theme_prop,
                  df.triad_country_freq_M$theme_freq_prop_M, na.rm=T))
corr.M

#Pearson correlation between EN and VI corpus
corr.EV = apa_print(cor.test(df.triad_country_freq_V$theme_freq_prop_V,
                   df.triad_country_freq_E$theme_freq_prop_E, na.rm=T))
corr.EM = apa_print(cor.test(df.triad_country_freq_M$theme_freq_prop_M,
                   df.triad_country_freq_E$theme_freq_prop_E, na.rm=T))
corr.MV = apa_print(cor.test(df.triad_country_freq_V$theme_freq_prop_V,
                   df.triad_country_freq_M$theme_freq_prop_M, na.rm=T))
```

```{r echo=FALSE, paged.print=FALSE, fig.cap ="Correlation between English corpus lexical co-occurrence and US responding, and Vietnamese corpus lexical co-occurrence and Vietnam responding."}
plotE + plotV + plotM
  plot_layout(ncol = 3)
```

We first conducted a Pearson correlation test between corresponding response data and corpus data. Looking at the raw lexical co-occurrence data, proportion of US thematic responding is moderately correlated to English corpus thematic proportion, `r corr.E$full_result`. Proportion of Vietnam thematic responding is moderately correlated to Vietnamese corpus thematic proportion, `r corr.V$full_result`. Proportion of China thematic responding is moderately correlated to Chinese corpus thematic proportion, `r corr.M$full_result`. 
There was a strong similarity signal between the thematic proportions in the English and Vietnamese corpora, `r corr.EV$full_result`, and the thematic proportions in the English and Mandarin corpora, `r corr.EM$full_result`. There was a moderate similarity signal between the proportions in the Mandarin and Vietnamese corpora, `r corr.MV$full_result.`

```{r Pearson correlation between corpus cosine distance and responding, warning=FALSE, include=FALSE}
df.triad_country_cos <- df %>%
  group_by(triad, country, theme_cosine_prop_E, theme_cosine_prop_V, theme_cosine_prop_M) %>%
  summarize(emp_theme_prop = mean(responses_theme))

df.triad_country_cos_E <- df.triad_country_cos %>%
  filter(country == "US")

plotE = ggplot(data = df.triad_country_cos_E, 
        mapping = aes(x = emp_theme_prop, 
                     y = theme_cosine_prop_E,
                     label = triad)) +
   geom_text() + 
   geom_smooth(method = "lm") +
   labs(x = "Proportion Thematic Chosen (US)", 
        y = "Proportion Thematic Predicted (English)") + 
   scale_y_reverse() + 
   xlim(0, 1) +
   ylim(0.8, 0.2) + 
  theme(axis.title = element_text(size=rel(0.75)))

df.triad_country_cos_V <- df.triad_country_cos %>%
  filter(country == "Vietnam")

plotV = ggplot(data = df.triad_country_cos_V, 
        mapping = aes(x = emp_theme_prop, 
                     y = theme_cosine_prop_V, 
                     label = triad)) +
   geom_text() + 
   geom_smooth(method = "lm") +
   labs(x = "Proportion Thematic Chosen (Vietnam)", 
        y = "Proportion Thematic Predicted (Vietnamese)") + 
   scale_y_reverse() +
   xlim(0, 1) +
   ylim(0.8, 0.2) + 
  theme(axis.title = element_text(size=rel(0.75)))

df.triad_country_cos_M <- df.triad_country_cos %>%
  filter(country == "China")

plotM = ggplot(data = df.triad_country_cos_M, 
        mapping = aes(x = emp_theme_prop, 
                     y = theme_cosine_prop_M, 
                     label = triad)) +
   geom_text() + 
   geom_smooth(method = "lm") +
   labs(x = "Proportion Thematic Chosen (China)", 
        y = "Proportion Thematic Predicted (Mandarin)") + 
   xlim(0, 1) +
   ylim(0.8, 0.2) + 
  theme(axis.title = element_text(size=rel(0.75)))

corr.E_cos = apa_print(cor.test(df.triad_country_cos_E$emp_theme_prop,
                      df.triad_country_cos_E$theme_cosine_prop_E, na.rm=T))

corr.V_cos = apa_print(cor.test(df.triad_country_cos_V$emp_theme_prop,
                      df.triad_country_cos_V$theme_cosine_prop_V, na.rm=T))

>>>>

---
title: "How to Make a Proceedings Paper Submission"
bibliography: library.bib
csl: apa6.csl
document-params: "10pt, letterpaper"

author-information: > 
    \author{{\large \bf Morton Ann Gernsbacher (MAG@Macc.Wisc.Edu)} \\ Department of Psychology, 1202 W. Johnson Street \\ Madison, WI 53706 USA
    \AND {\large \bf Sharon J.~Derry (SDJ@Macc.Wisc.Edu)} \\ Department of Educational Psychology, 1025 W. Johnson Street \\ Madison, WI 53706 USA}

abstract: >
  Is “cow” more closely related to “grass” or “chicken”? Speakers of different languages judge similarity in this context differently, but why? One possibility is that cultures co-varying with these languages induce variation in conceptualizations of similarity. Specifically, East Asian cultures may promote reasoning about thematic similarity, by which cow and grass are more related whereas Western cultures may bias similarity judgments toward taxonomic relations, like cow-chicken. This difference in notions of similarity is the consensus interpretation for cross-cultural variation in this paradigm. We consider, and provide evidence for, an alternative possibility, by which notions of similarity are equivalent across contexts, but the statistics of the environment vary. On this account, similarity judgments are guided by co-occurrence in experience, and observing or hearing about cows and grass or cows and chickens more often could induce preferences for the relevant grouping and account for apparent differences in notions of similarity across contexts.

keywords: >
    similarity; culture; language; semantics; lexical co-occurrence; variation

output: cogsci2016::cogsci_paper
#final-submission: \cogscifinalcopy
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, 
                      fig.pos = "tb", fig.path='figs/',
                      echo=F, warning=F, cache=F, 
                      message=F, sanitize = T)
```

```{r, libraries}
library(png)
library(grid)
library(ggplot2)
library(xtable)
```

@@

#r_refs("r-references.bib")
#r_refs("references/packages.bib")

@@

## Two-column images

You can read local images using png package for example and plot 
it like a regular plot using grid.raster from the grid package. 
With this method you have full control of the size of your image. **Note: Image must be in .png file format for the readPNG function to work.**

You might want to display a wide figure across both columns. To do this, you change the `fig.env` chunk option to `figure*`. To align the image in the center of the page, set `fig.align` option to `center`. To format the width of your caption text, you set the `num.cols.cap` option to `2`.

```{r 2-col-image, fig.env = "figure*", fig.pos = "h", fig.width=4, fig.height=2, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "This image spans both columns. And the caption text is limited to 0.8 of the width of the document."}
img <- png::readPNG("figs/walrus.png")
grid::grid.raster(img)
```

## One-column images

Single column is the default option, but if you want set it explicitly, set `fig.env` to `figure`. Notice that the `num.cols` option for the caption width is set to `1`.

```{r image, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=2, fig.height=2, set.cap.width=T, num.cols.cap=1, fig.cap = "One column image."}
img <- png::readPNG("figs/lab_logo_stanford.png")
grid::grid.raster(img)
```

## R Plots

You can use R chunks directly to plot graphs. And you can use latex floats in the
fig.pos chunk option to have more control over the location of your plot on the page. For more information on latex placement specifiers see **[here](https://en.wikibooks.org/wiki/LaTeX/Floats,_Figures_and_Captions)**

```{r plot, fig.env="figure", fig.pos = "H", fig.align = "center", fig.width=2, fig.height=2, fig.cap = "R plot" }
x <- 0:100
y <- 2 * (x + rnorm(length(x), sd = 3) + 3)

ggplot2::ggplot(data = data.frame(x, y), 
                aes(x = x, y = y)) + 
  geom_point() + 
  geom_smooth(method = "lm")
```

## Tables

Number tables consecutively; place the table number and title (in
10 point) above the table with one line space above the caption and
one line space below it, as in Table 1. You may float
tables to the top or bottom of a column, set wide tables across both
columns.

You can use the xtable function in the xtable package.

```{r xtable, results="asis"}
n <- 100
x <- rnorm(n)
y <- 2*x + rnorm(n)
out <- lm(y ~ x)

tab1 <- xtable::xtable(summary(out)$coef, digits=c(0, 2, 2, 1, 2), 
                       caption = "This table prints across one column.")

print(tab1, type="latex", comment = F, table.placement = "H")
```

# Acknowledgements

Place acknowledgments (including funding information) in a section at
the end of the paper.
